beastscriptr: BEAUti for R

### 2017-10-05 main.tex
Discussion

@@

beastscriptr allow for using BEAST2 from a scripted input file.

>>>>

beastscriptr has minimal support for calling BEAST2 from within R and does
so for testing purposes.

beastscript has minimal support for parsing and interpreting BEAST2 output files,
for that the RBeast package is recommended.

@@

beastscriptr successfully creates valid BEAST2 input files. Unlike BEAUti,
beascriptr allows for setting a fixed crown age.
